---
title: "F%$# Twitter. A corpus-based analysis of vulgar language on Twitter - Part 2: Data Processing and Usage Statistics"
author: "Martin Schweinberger"
date: "`r Sys.Date()`"
output: html_document
---


# Introduction

This document shows the analysis of swear words in the Australian, UK, and US Twitterspheres

# Preparation

Install packages

```{r inst, eval = F}
# install packages from CRAN
install.packages(c("dplyr", "here", "stringr", "quanteda", "tidytext", "sentimentr", "writexl", "ggplot2", "Hmisc", "countrycode", "ggimage", "cfa", "forcats"))

# install ggflags package from GitHub
install.packages("devtools")
devtools::install_github('rensa/ggflags')
```

Activate packages

```{r}
library(dplyr)
library(here)
library(stringr)
library(tidytext)
library(quanteda)
library(sentimentr)
library(writexl)
library(ggplot2)
library(Hmisc)
library(cfa)
library(countrycode)
library(ggflags)
library(forcats)  # For reordering
```

# Processing

Load data

```{r load}
twdat  <- base::readRDS(file = here::here("data", "twdat.rda"))
kwicdf <- base::readRDS(file = here::here("tables", "kwicdf_clean.rda"))
# inspect
str(twdat); str(kwicdf)
```



# Bad language overview
count swear words

```{r}
kwicdf %>%
  dplyr::group_by(lemma) %>%
  dplyr::summarize(freq = n()) %>%
  ungroup() %>%
  dplyr::mutate(total = sum(freq),
                percent = round(freq/total *100, 2)) %>%
  #dplyr::group_by(lemma) %>%
  #dplyr::summarize(freq = sum(freq)) %>%
  ggplot(aes(reorder(lemma, freq), freq)) +
  geom_bar(stat = "identity", fill = "gray30") +
  geom_text(aes(y = freq+7000, label = paste(freq, " (", percent, "%)", sep = "")), size = 2.5, col = "gray20") + 
  theme_bw() +
  labs(x = "", y = "Absolute frequency",
       title = "") +
  coord_flip(ylim = c(0, 55000)) +
  theme(panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())
# save
ggsave(here::here("images", "Fig1.png"), width = 15, height = 20, units = "cm", dpi = 600)
```

```{r}
kwicdf %>%
  dplyr::group_by(lemma) %>%
  dplyr::summarize(freq = n()) %>%
  ungroup() %>%
  dplyr::mutate(total = sum(freq),
                percent = round(freq/total *100, 2)) %>%
  dplyr::arrange(-percent) -> topvul
sum(head(topvul$percent))
```



find lemmas that occur with a specific frequency

```{r}
kwicdf %>%
  dplyr::group_by(code, lemma) %>%
  dplyr::summarize(freq = n()) %>%
  ungroup() %>%
  dplyr::mutate(total = sum(freq)) %>%
  dplyr::mutate(ptw = freq/total*1000000,
                lemma = ifelse(freq > 500, lemma, "other")) %>%
  dplyr::group_by(code, lemma) %>%
  dplyr::summarize(freq = sum(freq)) %>%
  dplyr::filter(lemma != "other") %>%
  dplyr::pull(lemma) -> lemmaredux
# inspect
lemmaredux
```



```{r}
twdat %>%
  dplyr::group_by(code) %>%
  dplyr::summarise(words = sum(words)) -> twdatsum
# inspect
twdatsum
```

```{r}
kwicsum <- kwicdf %>%
  dplyr::mutate(lemma = ifelse(lemma %in% lemmaredux, lemma, "other")) %>%
  dplyr::group_by(code, lemma) %>%
  dplyr::summarise(freq = n())
# inspect
kwicsum
```

```{r}
Fig2dat <- dplyr::left_join(twdatsum, kwicsum) %>%
  dplyr::mutate(pmw = round(freq/words*1000000, 3))
# inspect
Fig2dat
```

```{r}
Fig2dat %>%
  ggplot(aes(x = reorder(lemma, pmw), y = pmw, group = code, country = code)) +
  geom_flag(size = 3, position = position_jitter(width = 0.3, height = 0.3)) +
  coord_flip() +
  theme_bw() +
  theme(#panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  labs(y = "Relative Frequency (per million words)",
       x = "Vulgar lemma (only N > 500)")
# save
ggsave(here::here("images", "Fig2_new.png"), width = 15, height = 12, units = "cm", dpi = 600)
```



```{r}
Fig2dat %>%
  ggplot(aes(x = reorder(lemma, pmw), y = pmw, group = code, country = code)) +
  geom_flag() +
  coord_flip() +
  theme_bw()  +
  theme(panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) +
  labs(y = "Relative Frequency (per million words)", x = "Vulgar lemma (only N > 500)")
# save
ggsave(here::here("images", "Fig2.png"), width = 15, height = 12, units = "cm", dpi = 600)
```

# CFA

```{r}
kwicdf %>%
  dplyr::group_by(code, lemma) %>%
  dplyr::summarise(freq = n()) -> cfadat
configs <- cfadat %>%
  dplyr::select(code, lemma)
counts <- cfadat$freq
# perform cfa
cfa(configs, counts) -> cfares
cfares$table %>% as.data.frame() %>%
  dplyr::filter(sig.chisq == T)  %>%
  dplyr::mutate(type = ifelse(expected<n, "avoided", "preferred"),
                phi = sqrt(chisq/sum(cfadat$freq)),
                phi = ifelse(type == "avoided", phi, -phi))   %>%
  dplyr::arrange(-phi) %>%
  dplyr::select(-sig.chisq, -z, -p.z, -sig.z) -> cfaresdf
# save to disc
base::saveRDS(cfaresdf, file = here::here("tables", "cfaresdf.rda"))
# inspect
cfaresdf
```

## CFA US GB

```{r}
kwicdf %>%
  dplyr::filter(code == "gb"|code == "us") %>%
  dplyr::group_by(code, lemma) %>%
  dplyr::summarise(freq = n()) -> cfadat
configs <- cfadat %>%
  dplyr::select(code, lemma)
counts <- cfadat$freq
# perform cfa
cfa(configs, counts) -> cfares
cfares$table %>% as.data.frame() %>%
  dplyr::filter(sig.chisq == T)  %>%
  dplyr::mutate(type = ifelse(expected<n, "preferred", "avoided"),
                phi = sqrt(chisq/sum(cfadat$freq)),
                phi = ifelse(type == "avoided", -phi, phi))   %>%
  dplyr::arrange(-phi) %>%
  dplyr::select(-sig.chisq, -z, -p.z, -sig.z)   %>%
  dplyr::mutate(comp = "United States vs United Kingdom") -> cfausgb
# save to disc
base::saveRDS(cfausgb, file = here::here("tables", "cfausgb.rda"))
# inspect
cfausgb
```

## CFA AU US

```{r}
kwicdf %>%
  dplyr::filter(code == "au"|code == "us") %>%
  dplyr::group_by(code, lemma) %>%
  dplyr::summarise(freq = n()) -> cfadat
configs <- cfadat %>%
  dplyr::select(code, lemma)
counts <- cfadat$freq
# perform cfa
cfa(configs, counts) -> cfares
cfares$table %>% as.data.frame() %>%
  dplyr::filter(sig.chisq == T)  %>%
  dplyr::mutate(type = ifelse(expected<n, "preferred", "avoided"),
                phi = sqrt(chisq/sum(cfadat$freq)),
                phi = ifelse(type == "avoided", -phi, phi))   %>%
  dplyr::arrange(-phi) %>%
  dplyr::select(-sig.chisq, -z, -p.z, -sig.z)   %>%
  dplyr::mutate(comp = "United States vs Australia") -> cfausau
# save to disc
base::saveRDS(cfausau, file = here::here("tables", "cfausau.rda"))
# inspect
cfausau
```

## CFA AU GB

```{r}
kwicdf %>%
  dplyr::filter(code == "au"|code == "gb") %>%
  dplyr::group_by(code, lemma) %>%
  dplyr::summarise(freq = n()) -> cfadat
configs <- cfadat %>%
  dplyr::select(code, lemma)
counts <- cfadat$freq
# perform cfa
cfa(configs, counts) -> cfares
cfares$table %>% as.data.frame() %>%
  dplyr::filter(sig.chisq == T)  %>%
  dplyr::mutate(type = ifelse(expected<n, "preferred", "avoided"),
                phi = sqrt(chisq/sum(cfadat$freq)),
                phi = ifelse(type == "avoided", -phi, phi))   %>%
  dplyr::arrange(-phi) %>%
  dplyr::select(-sig.chisq, -z, -p.z, -sig.z)   %>%
  dplyr::mutate(comp = "Australia vs United Kingdom") -> cfaaugb
# save to disc
base::saveRDS(cfaaugb, file = here::here("tables", "cfaaugb.rda"))
# inspect
cfaaugb
```


## Fig5_cfa

```{r}
Fig5dat <- rbind(cfausgb, cfausau) %>%
  dplyr::mutate(label = stringr::str_replace_all(label, "gb", "uk")) %>%
  dplyr::select(-chisq, -p.chisq, -Q)
Fig5dat
```

```{r}
Fig5dat %>%
  ggplot(aes(y = phi, x = reorder(label, phi), fill = , fill = phi > 0)) +
  geom_bar(stat = "identity") +
  geom_text(aes(
        y = ifelse(phi > 0, phi - 0.02, phi + 0.02),
        label = round(phi, 2)
    ), color = "gray20", size = 3) +
  facet_wrap(~comp, scales = "free") +
  coord_flip() +
  scale_fill_manual(values = c("TRUE" = "gray80", "FALSE" = "gray50")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none") +
  labs(x = "Configuration\n(region + lemma)", y = "Phi-coefficient")
# save
ggsave(here::here("images", "Fig5_cfa.png"), width = 15, height = 12, units = "cm", dpi = 600)
```

# Collostructional Analysis

```{r}
head(kwicdf)
kwicdf %>%
  dplyr::mutate(code = ifelse(code == "gb", "uk", code)) %>%
  dplyr::group_by(code, lemma) %>%
  dplyr::summarise(freq = n()) %>%
  tidyr::spread(code, freq) %>%
  tidyr::replace_na(list(au = 0, uk = 0, us = 0)) %>%
  dplyr::rename(token = lemma) -> collodat
# inspect
collodat
```

## US vs UK

```{r}
collodat %>%
  dplyr::select(-au)  %>%
  dplyr::rename(text1 = uk,
                text2 = us) %>%
    dplyr::mutate(
        text1 = as.numeric(text1),
        text2 = as.numeric(text2)
    ) %>%
    dplyr::mutate(
        C1 = sum(text1),
        C2 = sum(text2),
        N = C1 + C2
    ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(
        R1 = text1 + text2,
        R2 = N - R1,
        O11 = text1,
        O11 = ifelse(O11 == 0, O11 + 1, O11),
        O12 = R1 - O11,
        O12 = ifelse(O12 < 0, 0, O12),
        O21 = C1 - O11,
        O22 = C2 - O12
    ) %>%
    dplyr::mutate(
        E11 = (R1 * C1) / N,
        E12 = (R1 * C2) / N,
        E21 = (R2 * C1) / N,
        E22 = (R2 * C2) / N
    ) %>%
    dplyr::select(-text1, -text2) -> stats_tb2
# inspect
stats_tb2
```


```{r}
stats_tb2 %>%
    # determine number of rows
    dplyr::mutate(Rws = nrow(.)) %>%
    # work row-wise
    dplyr::rowwise() %>%
    # calculate fishers' exact test
    dplyr::mutate(p = as.vector(unlist(fisher.test(matrix(c(O11, O12, O21, O22),
        ncol = 2, byrow = T
    ))[1]))) %>%
    # extract descriptives
    dplyr::mutate(
        ptw_target = O11 / C1 * 1000,
        ptw_ref = O12 / C2 * 1000
    ) %>%
    # extract x2 statistics
    dplyr::mutate(X2 = (O11 - E11)^2 / E11 + (O12 - E12)^2 / E12 + (O21 - E21)^2 / E21 + (O22 - E22)^2 / E22) %>%
    # extract keyness measures
    dplyr::mutate(
        phi = sqrt((X2 / N)),
        MI = log2(O11 / E11),
        t.score = (O11 - E11) / sqrt(O11),
        PMI = log2((O11 / N) / ((O11 + O12) / N) *
            ((O11 + O21) / N)),
        DeltaP = (O11 / R1) - (O21 / R2),
        LogOddsRatio = log(((O11 + 0.5) * (O22 + 0.5)) / ((O12 + 0.5) * (O21 + 0.5))),
        G2 = 2 * ((O11 + 0.001) * log((O11 + 0.001) / E11) + (O12 + 0.001) * log((O12 + 0.001) / E12) + O21 * log(O21 / E21) + O22 * log(O22 / E22)),

        # traditional keyness measures
        RateRatio = ((O11 + 0.001) / (C1 * 1000)) / ((O12 + 0.001) / (C2 * 1000)),
        RateDifference = (O11 / (C1 * 1000)) - (O12 / (C2 * 1000)),
        DifferenceCoefficient = RateDifference / sum((O11 / (C1 * 1000)), (O12 / (C2 * 1000))),
        OddsRatio = ((O11 + 0.5) * (O22 + 0.5)) / ((O12 + 0.5) * (O21 + 0.5)),
        LLR = 2 * (O11 * (log((O11 / E11)))),
        RDF = abs((O11 / C1) - (O12 / C2)),
        PDiff = abs(ptw_target - ptw_ref) / ((ptw_target + ptw_ref) / 2) * 100,
        SignedDKL = sum(ifelse(O11 > 0, O11 * log(O11 / ((O11 + O12) / 2)), 0) - ifelse(O12 > 0, O12 * log(O12 / ((O11 + O12) / 2)), 0))
    ) %>%
    # determine Bonferroni corrected significance
    dplyr::mutate(Sig_corrected = dplyr::case_when(
        p / Rws > .05 ~ "n.s.",
        p / Rws > .01 ~ "p < .05*",
        p / Rws > .001 ~ "p < .01**",
        p / Rws <= .001 ~ "p < .001***",
        T ~ "N.A."
    )) %>%
    # round p-value
    dplyr::mutate(
        p = round(p, 5),
        type = ifelse(E11 > O11, "antitype", "type"),
        phi = ifelse(E11 > O11, -phi, phi),
        G2 = ifelse(E11 > O11, -G2, G2)
    ) %>%
    # filter out non significant results
    dplyr::filter(Sig_corrected != "n.s.") %>%
    # arrange by phi
    dplyr::arrange(-phi) %>%
    # remove superfluous columns
    dplyr::select(-any_of(c(
        "TermCoocFreq", "AllFreq", "NRows",
        "R1", "R2", "C1", "C2", "E12", "E21",
        "E22", "upp", "low", "op", "t.score", "z.score", "Rws"
    ))) %>%
    dplyr::relocate(any_of(c(
        "token", "type", "Sig_corrected", "O11", "O12",
        "ptw_target", "ptw_ref", "G2", "RDF", "RateRatio",
        "RateDifference", "DifferenceCoefficient", "LLR", "SignedDKL",
        "PDiff", "LogOddsRatio", "MI", "PMI", "phi", "X2",
        "OddsRatio", "DeltaP", "p", "E11", "O21", "O22"
    ))) %>%
  dplyr::mutate(code = ifelse(phi > 0, "gb", "us")) -> assoc_tb3
# inspect
assoc_tb3
```

```{r}
# get top 10 keywords for text 1
top <- assoc_tb3 %>%
    dplyr::ungroup() %>%
    dplyr::slice_head(n = 10)
# get top 10 keywords for text 2
bot <- assoc_tb3 %>%
    dplyr::ungroup() %>%
    dplyr::slice_tail(n = 10)
# combine into table
rbind(top, bot)  %>%
  dplyr::mutate(comp = "United States vs United Kingdom")-> collousuk

collousuk %>%
    # create a ggplot
    ggplot(aes(x = reorder(token, phi, mean), y = phi, label = phi, fill = type, country = code)) +
    # add a bar plot using the 'phi' values
    geom_bar(stat = "identity") +
    # add text labels above the bars with rounded 'phi' values
    geom_text(aes(
        y = ifelse(phi > 0, phi - 0.02, phi - 0.02),
        label = round(phi, 3)
    ), color = "gray20", size = 3) +
    geom_flag(aes(y = 0)) +
    # flip the coordinates to have horizontal bars
    coord_flip() +
    # set the theme to a basic white and black theme
    theme_bw() +
    # remove legend
    theme(legend.position = "none") +
    # define colors
    scale_fill_manual(values = c("gray50", "gray80")) +
    # set the x-axis label to "Token" and y-axis label to "Keyness (G2)"
    labs(title = "", x = "Vulgar lemma", y = "Phi-coefficient")
```

## US vs AU

```{r}
collodat %>%
  dplyr::select(-uk)  %>%
  dplyr::rename(text1 = au,
                text2 = us) %>%
    dplyr::mutate(
        text1 = as.numeric(text1),
        text2 = as.numeric(text2)
    ) %>%
    dplyr::mutate(
        C1 = sum(text1),
        C2 = sum(text2),
        N = C1 + C2
    ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(
        R1 = text1 + text2,
        R2 = N - R1,
        O11 = text1,
        O11 = ifelse(O11 == 0, O11 + 1, O11),
        O12 = R1 - O11,
        O12 = ifelse(O12 < 0, 0, O12),
        O21 = C1 - O11,
        O22 = C2 - O12
    ) %>%
    dplyr::mutate(
        E11 = (R1 * C1) / N,
        E12 = (R1 * C2) / N,
        E21 = (R2 * C1) / N,
        E22 = (R2 * C2) / N
    ) %>%
    dplyr::select(-text1, -text2) -> stats_tb2
# inspect
stats_tb2
```


```{r}
stats_tb2 %>%
    # determine number of rows
    dplyr::mutate(Rws = nrow(.)) %>%
    # work row-wise
    dplyr::rowwise() %>%
    # calculate fishers' exact test
    dplyr::mutate(p = as.vector(unlist(fisher.test(matrix(c(O11, O12, O21, O22),
        ncol = 2, byrow = T
    ))[1]))) %>%
    # extract descriptives
    dplyr::mutate(
        ptw_target = O11 / C1 * 1000,
        ptw_ref = O12 / C2 * 1000
    ) %>%
    # extract x2 statistics
    dplyr::mutate(X2 = (O11 - E11)^2 / E11 + (O12 - E12)^2 / E12 + (O21 - E21)^2 / E21 + (O22 - E22)^2 / E22) %>%
    # extract keyness measures
    dplyr::mutate(
        phi = sqrt((X2 / N)),
        MI = log2(O11 / E11),
        t.score = (O11 - E11) / sqrt(O11),
        PMI = log2((O11 / N) / ((O11 + O12) / N) *
            ((O11 + O21) / N)),
        DeltaP = (O11 / R1) - (O21 / R2),
        LogOddsRatio = log(((O11 + 0.5) * (O22 + 0.5)) / ((O12 + 0.5) * (O21 + 0.5))),
        G2 = 2 * ((O11 + 0.001) * log((O11 + 0.001) / E11) + (O12 + 0.001) * log((O12 + 0.001) / E12) + O21 * log(O21 / E21) + O22 * log(O22 / E22)),

        # traditional keyness measures
        RateRatio = ((O11 + 0.001) / (C1 * 1000)) / ((O12 + 0.001) / (C2 * 1000)),
        RateDifference = (O11 / (C1 * 1000)) - (O12 / (C2 * 1000)),
        DifferenceCoefficient = RateDifference / sum((O11 / (C1 * 1000)), (O12 / (C2 * 1000))),
        OddsRatio = ((O11 + 0.5) * (O22 + 0.5)) / ((O12 + 0.5) * (O21 + 0.5)),
        LLR = 2 * (O11 * (log((O11 / E11)))),
        RDF = abs((O11 / C1) - (O12 / C2)),
        PDiff = abs(ptw_target - ptw_ref) / ((ptw_target + ptw_ref) / 2) * 100,
        SignedDKL = sum(ifelse(O11 > 0, O11 * log(O11 / ((O11 + O12) / 2)), 0) - ifelse(O12 > 0, O12 * log(O12 / ((O11 + O12) / 2)), 0))
    ) %>%
    # determine Bonferroni corrected significance
    dplyr::mutate(Sig_corrected = dplyr::case_when(
        p / Rws > .05 ~ "n.s.",
        p / Rws > .01 ~ "p < .05*",
        p / Rws > .001 ~ "p < .01**",
        p / Rws <= .001 ~ "p < .001***",
        T ~ "N.A."
    )) %>%
    # round p-value
    dplyr::mutate(
        p = round(p, 5),
        type = ifelse(E11 > O11, "antitype", "type"),
        phi = ifelse(E11 > O11, -phi, phi),
        G2 = ifelse(E11 > O11, -G2, G2)
    ) %>%
    # filter out non significant results
    dplyr::filter(Sig_corrected != "n.s.") %>%
    # arrange by phi
    dplyr::arrange(-phi) %>%
    # remove superfluous columns
    dplyr::select(-any_of(c(
        "TermCoocFreq", "AllFreq", "NRows",
        "R1", "R2", "C1", "C2", "E12", "E21",
        "E22", "upp", "low", "op", "t.score", "z.score", "Rws"
    ))) %>%
    dplyr::relocate(any_of(c(
        "token", "type", "Sig_corrected", "O11", "O12",
        "ptw_target", "ptw_ref", "G2", "RDF", "RateRatio",
        "RateDifference", "DifferenceCoefficient", "LLR", "SignedDKL",
        "PDiff", "LogOddsRatio", "MI", "PMI", "phi", "X2",
        "OddsRatio", "DeltaP", "p", "E11", "O21", "O22"
    ))) %>%
  dplyr::mutate(code = ifelse(phi > 0, "au", "us")) %>%
  dplyr::filter(!is.na(phi)) -> assoc_tb3
# inspect
assoc_tb3
```


```{r}
# get top 10 keywords for text 1
top <- assoc_tb3 %>%
    dplyr::ungroup() %>%
   #dplyr::filter(!is.na(phi)) %>%
    dplyr::slice_head(n = 10)
# get top 10 keywords for text 2
bot <- assoc_tb3 %>%
    dplyr::ungroup() %>%
    dplyr::slice_tail(n = 10)
# combine into table
rbind(top, bot)  %>%
  dplyr::mutate(comp = "Australia vs United States")-> collousau

collousau %>%
    # create a ggplot
    ggplot(aes(x = reorder(token, phi, mean), y = phi, label = phi, fill = type, country = code)) +
    # add a bar plot using the 'phi' values
    geom_bar(stat = "identity") +
    # add text labels above the bars with rounded 'phi' values
    geom_text(aes(
        y = ifelse(phi > 0, phi + 0.02, phi - 0.02),
        label = round(phi, 3)
    ), color = "gray20", size = 3) +
    geom_flag(aes(y = 0)) +
    # flip the coordinates to have horizontal bars
    coord_flip() +
    # set the theme to a basic white and black theme
    theme_bw() +
    # remove legend
    theme(legend.position = "none") +
    # define colors
    scale_fill_manual(values = c("gray50", "gray80")) +
    # set the x-axis label to "Token" and y-axis label to "Keyness (G2)"
    labs(title = "", x = "Vulgar lemma", y = "Phi-coefficient")
```

## GB vs AU

```{r}
collodat %>%
  dplyr::select(-us)  %>%
  dplyr::rename(text1 = uk,
                text2 = au) %>%
    dplyr::mutate(
        text1 = as.numeric(text1),
        text2 = as.numeric(text2)
    ) %>%
    dplyr::mutate(
        C1 = sum(text1),
        C2 = sum(text2),
        N = C1 + C2
    ) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(
        R1 = text1 + text2,
        R2 = N - R1,
        O11 = text1,
        O11 = ifelse(O11 == 0, O11 + 1, O11),
        O12 = R1 - O11,
        O12 = ifelse(O12 < 0, 0, O12),
        O21 = C1 - O11,
        O22 = C2 - O12
    ) %>%
    dplyr::mutate(
        E11 = (R1 * C1) / N,
        E12 = (R1 * C2) / N,
        E21 = (R2 * C1) / N,
        E22 = (R2 * C2) / N
    ) %>%
    dplyr::select(-text1, -text2) -> stats_tb2
# inspect
stats_tb2
```



```{r}
stats_tb2 %>%
    # determine number of rows
    dplyr::mutate(Rws = nrow(.)) %>%
    # work row-wise
    dplyr::rowwise() %>%
    # calculate fishers' exact test
    dplyr::mutate(p = as.vector(unlist(fisher.test(matrix(c(O11, O12, O21, O22),
        ncol = 2, byrow = T
    ))[1]))) %>%
    # extract descriptives
    dplyr::mutate(
        ptw_target = O11 / C1 * 1000,
        ptw_ref = O12 / C2 * 1000
    ) %>%
    # extract x2 statistics
    dplyr::mutate(X2 = (O11 - E11)^2 / E11 + (O12 - E12)^2 / E12 + (O21 - E21)^2 / E21 + (O22 - E22)^2 / E22) %>%
    # extract keyness measures
    dplyr::mutate(
        phi = sqrt((X2 / N)),
        MI = log2(O11 / E11),
        t.score = (O11 - E11) / sqrt(O11),
        PMI = log2((O11 / N) / ((O11 + O12) / N) *
            ((O11 + O21) / N)),
        DeltaP = (O11 / R1) - (O21 / R2),
        LogOddsRatio = log(((O11 + 0.5) * (O22 + 0.5)) / ((O12 + 0.5) * (O21 + 0.5))),
        G2 = 2 * ((O11 + 0.001) * log((O11 + 0.001) / E11) + (O12 + 0.001) * log((O12 + 0.001) / E12) + O21 * log(O21 / E21) + O22 * log(O22 / E22)),

        # traditional keyness measures
        RateRatio = ((O11 + 0.001) / (C1 * 1000)) / ((O12 + 0.001) / (C2 * 1000)),
        RateDifference = (O11 / (C1 * 1000)) - (O12 / (C2 * 1000)),
        DifferenceCoefficient = RateDifference / sum((O11 / (C1 * 1000)), (O12 / (C2 * 1000))),
        OddsRatio = ((O11 + 0.5) * (O22 + 0.5)) / ((O12 + 0.5) * (O21 + 0.5)),
        LLR = 2 * (O11 * (log((O11 / E11)))),
        RDF = abs((O11 / C1) - (O12 / C2)),
        PDiff = abs(ptw_target - ptw_ref) / ((ptw_target + ptw_ref) / 2) * 100,
        SignedDKL = sum(ifelse(O11 > 0, O11 * log(O11 / ((O11 + O12) / 2)), 0) - ifelse(O12 > 0, O12 * log(O12 / ((O11 + O12) / 2)), 0))
    ) %>%
    # determine Bonferroni corrected significance
    dplyr::mutate(Sig_corrected = dplyr::case_when(
        p / Rws > .05 ~ "n.s.",
        p / Rws > .01 ~ "p < .05*",
        p / Rws > .001 ~ "p < .01**",
        p / Rws <= .001 ~ "p < .001***",
        T ~ "N.A."
    )) %>%
    # round p-value
    dplyr::mutate(
        p = round(p, 5),
        type = ifelse(E11 > O11, "antitype", "type"),
        phi = ifelse(E11 > O11, -phi, phi),
        G2 = ifelse(E11 > O11, -G2, G2)
    ) %>%
    # filter out non significant results
    dplyr::filter(Sig_corrected != "n.s.") %>%
    # arrange by phi
    dplyr::arrange(-phi) %>%
    # remove superfluous columns
    dplyr::select(-any_of(c(
        "TermCoocFreq", "AllFreq", "NRows",
        "R1", "R2", "C1", "C2", "E12", "E21",
        "E22", "upp", "low", "op", "t.score", "z.score", "Rws"
    ))) %>%
    dplyr::relocate(any_of(c(
        "token", "type", "Sig_corrected", "O11", "O12",
        "ptw_target", "ptw_ref", "G2", "RDF", "RateRatio",
        "RateDifference", "DifferenceCoefficient", "LLR", "SignedDKL",
        "PDiff", "LogOddsRatio", "MI", "PMI", "phi", "X2",
        "OddsRatio", "DeltaP", "p", "E11", "O21", "O22"
    ))) %>%
  dplyr::mutate(code = ifelse(phi > 0, "gb", "au"))  %>%
  dplyr::filter(!is.na(phi))-> assoc_tb3
# inspect
assoc_tb3
```


```{r}
# get top 10 keywords for text 1
top <- assoc_tb3 %>%
    dplyr::ungroup() %>%
    dplyr::slice_head(n = 10)
# get top 10 keywords for text 2
bot <- assoc_tb3 %>%
    dplyr::ungroup() %>%
    dplyr::slice_tail(n = 10)
# combine into table
rbind(top, bot) %>%
  dplyr::mutate(comp = "Australia vs United Kingdom") -> colloauuk

colloauuk %>%
    # create a ggplot
    ggplot(aes(x = reorder(token, phi, mean), y = phi, label = phi, fill = type, country = code)) +
    # add a bar plot using the 'phi' values
    geom_bar(stat = "identity") +
    # add text labels above the bars with rounded 'phi' values
    geom_text(aes(
        y = ifelse(phi > 0, phi + 0.02, phi - 0.02),
        label = round(phi, 3)
    ), color = "gray20", size = 3) +
    geom_flag(aes(y = 0)) +
    # flip the coordinates to have horizontal bars
    coord_flip() +
    # set the theme to a basic white and black theme
    theme_bw() +
    # remove legend
    theme(legend.position = "none") +
    # define colors
    scale_fill_manual(values = c("gray50", "gray80")) +
    # set the x-axis label to "Token" and y-axis label to "Keyness (G2)"
    labs(title = "", x = "Vulgar lemma", y = "Phi-coefficient")
```


## Fig5 collo

```{r}
Fig5dat2 <- rbind(colloauuk, collousau, collousuk) %>%
  dplyr::filter(!is.na(phi)) %>%
  dplyr::group_by(comp) %>%
  mutate(token = fct_reorder2(token, comp, -phi)) %>%
  dplyr::ungroup()
Fig5dat2 %>%
    # create a ggplot
    ggplot(aes(x = token, y = phi, label = phi, fill = type, country = code)) +
    # add a bar plot using the 'phi' values
    geom_bar(stat = "identity") +
    # add text labels above the bars with rounded 'phi' values
    geom_text(aes(
        y = ifelse(phi > 0, phi + 0.03, phi - 0.03),
        label = round(phi, 3)
    ), color = "gray20", size = 3) +
    geom_flag(aes(y = 0)) +
    facet_wrap(~comp, scales = "free_y") +
    # flip the coordinates to have horizontal bars
    coord_flip(ylim = c(-0.15, 0.2)) +
    # set the theme to a basic white and black theme
    theme_bw() +
    # remove legend
    theme(legend.position = "none") +
    # define colors
    scale_fill_manual(values = c("gray50", "gray80")) +
    # set the x-axis label to "Token" and y-axis label to "Keyness (G2)"
    labs(title = "", x = "Vulgar lemma", y = "Phi-coefficient")
# save
ggsave(here::here("images", "Fig5.png"), width = 21, height = 12, units = "cm", dpi = 600)
```

```{r}
library(dplyr)
library(ggplot2)
library(forcats)
library(ggflags)
library(tidytext) # for reorder_within

# Combine datasets and prepare
Fig5dat2 <- bind_rows(colloauuk, collousau, collousuk) %>%
  filter(!is.na(phi))

# Plot with per-facet ordering
ggplot(Fig5dat2, aes(
    x = reorder_within(token, phi, comp), 
    y = phi, 
    label = phi, 
    fill = type,
    country = code
  )) +
  geom_bar(stat = "identity") +
  geom_text(aes(
    y = ifelse(phi > 0, phi + 0.015, phi - 0.015), 
    label = round(phi, 3)
  ), color = "gray20", size = 3) +
  geom_flag(aes(y = 0), size = 5) +
  facet_wrap(~comp, scales = "free_y") +
  coord_flip(ylim = c(-0.15, 0.2)) +
  scale_x_reordered() +  # Corrects x-axis ordering per facet
  theme_bw() +
  theme(
    legend.position = "none",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_fill_manual(values = c("gray50", "gray80")) +
  labs(
    title = NULL,
    x = "Vulgar lemma",
    y = "Phi-coefficient"
  )
# save
ggsave(here::here("images", "Fig5_new.png"), width = 21, height = 12, units = "cm", dpi = 600)
```



# Outro

```{r}
sessionInfo()
```

