---
title: "F%$# Twitter. A corpus-based analysis of vulgar language on Twitter - Part 1: Data Preparation, Extraction, and Processing"
author: "Martin Schweinberger"
date: "`r Sys.Date()`"
output: html_document
---


# Introduction

This document shows the analysis of swear words in the Australian, UK, and US Twitterspheres

# Preparation

Install packages

```{r inst, eval = F}
# install packages from CRAN
install.packages(c("dplyr", "here", "stringr", "quanteda", "tidytext", "sentimentr", "writexl", "ggplot2", "Hmisc", "countrycode", "ggimage"))

# install ggflags from GitHub
install.packages("devtools")
devtools::install_github('rensa/ggflags')
```

Activate packages

```{r}
library(dplyr)
library(here)
library(stringr)
library(tidytext)
library(quanteda)
library(sentimentr)
library(writexl)
library(ggplot2)
library(Hmisc)
library(countrycode)
library(ggflags)
```

# Processing

Load data

```{r load}
# Read and tag datasets
au <- read.csv(file.path("data/geo_AU_filtered_candidate_timelines.csv")) %>%
  mutate(var = "au")

gb <- read.csv(file.path("data/geo_GB_filtered_candidate_timelines.csv")) %>%
  mutate(var = "gb")

us <- read.csv(file.path("data/geo_US_filtered_candidate_timelines.csv")) %>%
  mutate(var = "us")

# Combine datasets
tw_raw <- bind_rows(au, gb, us)

# Inspect
glimpse(tw_raw)
# inspect
str(tw_raw)
```


Cleaning text

```{r clean1}
twdat_raw <- tw_raw %>%
  mutate(
    # Clean text
    cleantext = text %>%
      str_replace_all(fixed("\n"), " ") %>%                   # remove newlines
      str_replace_all("http.*?\\s|http.*?$|@.*?\\s", " ") %>% # remove URLs & mentions
      str_squish(),                                           # trim spaces
    
    # Lowercase version
    ltext = tolower(cleantext),
    
    # Country and code variables
    country = case_when(
      var == "au" ~ "AU",
      var == "gb" ~ "GB",
      var == "us" ~ "US",
      TRUE        ~ var
    ),
    code = tolower(country),
    
    # Words-only version
    wordsonly = cleantext %>%
      str_replace_all("\\W", " ") %>%
      str_squish(),
    
    # Word count
    words = lengths(quanteda::tokenize_fastestword(wordsonly))
  ) %>%
  group_by(code) %>%
  mutate(docname = paste0("text", row_number())) %>%
  ungroup()

# Inspect
glimpse(twdat_raw)
```


Remove non-English (based on Twitters language identification)


```{r}
twdat <- twdat_raw #%>%
  # remove non-english tweets
  #dplyr::filter(lang == "en")
```

compare twdat before and after removing non-English data

```{r eval = F}
tb1 <- twdat_raw %>%
  dplyr::group_by(var) %>%
  dplyr::summarise(words = sum(words),
                   tweets = n(),
                   status= "before revoval")

tb2 <- twdat %>%
  dplyr::group_by(var) %>%
  dplyr::summarise(words = sum(words),
                   tweets = n(),
                   status= "after revoval")
tb <- rbind(tb1, tb2)
# inspect
tb
```



```{r}
audf <- twdat %>% dplyr::filter(code == "au")
gbdf <- twdat %>% dplyr::filter(code == "gb")
usdf <- twdat %>% dplyr::filter(code == "us")
# save data
base::saveRDS(audf, file = here::here("data", "audf.rda"))
base::saveRDS(gbdf, file = here::here("data", "gbdf.rda"))
base::saveRDS(usdf, file = here::here("data", "usdf.rda"))
```



# Save and load

```{r}
# save data
base::saveRDS(twdat, file = here::here("data", "twdat.rda"))
twdat  <- base::readRDS(file = here::here("data", "twdat.rda"))
# inspect
str(twdat); head(twdat)
```

# Regex

define regex lists

The regex list represents is based on:

List of Bad Words, February 2025.
http://www.noswearing.com/dictionary/.

BannedWordList.com - a resource for web
administrators, March 2013.
http://www.bannedwordlist.com/.

McEnery, Anthony. 2006. Swearing in English: Bad Language, Purity and Power from 1586 to the Present. New York: Routledge. 

Thelwall, Mike. 2008. “Fk Yea I Swear: Cursing and Gender in MySpace.” Corpora 3 (1): 83–107. doi:10.3366/E1749503208000087. 

Coats, S. (2021). ‘Bad language’ in the Nordics: Profanity and gender in a social media corpus. Acta Linguistica Hafniensia, 53(1), 22–57. https://doi.org/10.1080/03740463.2021.1871218

Love, R. (2021). Swearing in informal spoken English: 1990s–2010s. Text & Talk, 41(5-6), 739-762.

Schweinberger, M. & K. Burridge (2025). Vulgarity in Online Discourse around the English-Speaking World. Lingua 321: 103946. (SJR: Q1) https://doi.org/10.1016/j.lingua.2025.103946

After reviewing the items deemed vulgar in the above publications, we decided which to include as we did not consider all elements in the publications as vulgar. The items we thus deemed as vulgar after reviewing are listed below. 

arse, arsehole, ass, asshole, bastard, beaner, bellend, bimbo, bitch, bloody,
bollock, boner, bonk, boob, bugger, bullshit, butt, butthead, butthole, chink, 
cock, coon, crap, cum, cunt, damn, darkie, dick, dike, dildo, dipshit, dork, 
eff, fag, fanny, fart, feck, frig, fuck, gash, gook, hell, hussy, idiot, 
jackass, jap, jerk, jiss, jug, kike, knocker, lesbo, minger, moron, 
motherfucker, muff, nonce, nympho, pecker, pedo, pikey, pimp, piss,  
poofter,  prick, puke, pussy, queef, retard,  shag, shit, shite, skank, 
slag, slut, sod, spastic, tit, tosser, tranny, turd, twat, wank, 
whore, online (such as wtf, lmao, etc)

The regular expression list below is designed to capture these and variants of these elements.

Vector of regular expressions for detecting vulgar language and obfuscations

```{r eval = T}
patterns <- c(
  # "arsehole/s"
  "\\b(dumb|stupid|lazy|worthless|useless|brain|dead|jack)*[a@4äáå]r[s5$§z][e3€ëéê][h]?[o0øöóõ]*[l1£][e3€ëéê]*[s5$§z]*\\b",

  # "ass/asshole/s"
  "\\b(dumb|stupid|lazy|worthless|useless|brain|dead|jack)*[a@4äáå][s5$§z]{2,}[h]?[o0øöóõ]*[l1|£][e3€ëéê]*[s5$§z]*\\b",

  # "bitch"
  "\\b[b8ß|3][i1!|ïíì]+[a@4äáå]*[t7+†][c¢©(][h](es|ez|ing|ed)*\\b",

  # "bastard"
  "\\b[b8ß|3][a@4äáå][s5$§z][t7+†][a@4äáå]r[d][o]*(s|z)*\\b",

  # "beaner"
  "\\b[b8ß|3][e3€ëéê][a@4äáå]n[e3€ëéê]r(s|z)*\\b",

  # "bellend"
  "\\b[b8ß|3][e3€ëéê]ll[e3€ëéê]nd(s|z)*\\b",

  # "bimbo"
  "\\b[b8ß|3][1!|ïíì]mb[o0øöóõ](s|z)*\\b",

  # "bloody"
  "\\bbl[o0øöóõ]{2,}d[iy¥](ed)*\\b",

  # "bollocks"
  "\\b[8ß|3][o0øöóõ]ll[o0øöóõiïíì][xc¢©(k|<{(]+[s5$§z]?\\b",

  # "boner"
  "\\bboner[s]*\\b",

  # "bonk"
  "\\b[8ß|3][o0øöóõ]n[k|<{(](in|ing)*\\b",

  # "boobs"
  "\\b[8ß|3][o0øöóõ]{2,}[b8ß|3][ie]*[s5$§z]?\\b",

  # "bugger"
  "\\b[8ß|3][u|µüúû]gg[e3€ëéê]r(ing|s|z)*\\b",

  # "bullshit"
  "\\b[b8ß|3][u|µüúû]ll[s5$§z]h[1!|ïíì]+[t7+†]*\\b",

  # "butt"
  "\\b[b8ß3][uµüúû][t7+†][t7+†][sz]*(face|head|wit|whipe|hole|h)*[hl]*[sz]*\\b",

  # "damn"
  "\\b(god)*damn\\b",

  # "darkie"
  "\\bdarki(es)*\\b",

  # "dike"
  "\\b(bull)*d[iy]*ke(s|z)*\\b",

  # "dildo"
  "\\bdildo(s|z)*\\b",

  # "dork"
  "\\bdork(s|z)*\\b",

  # "eff"
  "\\beff(ing|in|ed|d)*\\b",


  # "fanny"
  "\\bfann(y|ies)+\\b",

  # "fart"
  "\\bfart(s|z|ing|in|ed)*\\b",

  # "frig"
  "\\bfrig(g|gin|ging|ged|gs)*\\b",

  # Detects "fuck" variations
  "\\b(cluster|head|mother|motha|mutha|mada|cock|mom|mum|daddy|father|sister|brother)*[f=ƒ][uµüúû|@a4äáå|e3€ëéê|o0øöóõ|*]*[c¢©(]*[k|<{(][e3€ëéê]*[r]*(head|face|wit|ing|er|a|ed|ers|az)*\\b",
  "\\b[f=ƒ][c¢©(*k<{(uµüúû*]+(ing|er|a|ed|ers|az)*\\b",

  # Detects "fuck" variations as 'f'
  "\\bf\\b",

  # "gash"
  "\\bgash\\b",

  # "gook"
  "\\bg[o]*ok(s|z)*\\b",

  # "idiot"
  "\\bidiot(s|z)*\\b",

  # "jackass"
  "\\bjacka[s5$§z][s5$§z]\\b",

  # "jap"
  "\\bjap[zs]*\\b",

  # "jerk"
  "\\bjerk(s|z|in|ing|ed)*\\b",

  # "jiss"
  "\\bji[s5$§z][s5$§z]+\\b",

  # "jug"
  "\\bjug[g]*[s5$§z]*\\b",

  # "shit"
  "\\b[(dip)]*[s5$§z]h[1!|ïíì]+[t7+†]*(ing|e|in|er|a|ed|ers|az|s|z)*\\b",

  # Online variants

  # Knock the f*** out
  "\\bktfo\\b",

  # Shut the f*** up
  "\\bstfu\\b",

  # Get the f*** out
  "\\bgtfo\\b",

  # Not giving a f***
  "\\bngaf\\b",

  # Don't give a f***
  "\\bdgaf\\b",

  # For f***'s sake
  "\\bffs\\b",

  # F*** my life
  "\\bfml\\b",

  # Oh my f***ing god
  "\\bomfg\\b",

  # As f***
  "\\baf\\b",

  # The f***
  "\\btf\\b",

  # What the f***
  "\\bwtf\\b",

  # Laughing my ass off
  "\\blmao\\b",

  # Laughing my f***ing ass off
  "\\blmfao\\b",

  # Rolling on floor laughing
  "\\brofl\\b",

  # "chink"
  "\\bch[i]*nk[zs]*\\b",

  # "coon"
  "\\bcoon[zs]*\\b",

  # "crap"
  "\\b[bull]*crap(ping|ped|s|z|pin)*\\b",

  # "cum"
  "\\bcum(ming)*\\b",

  # "cock"
  "\\bc[o0øöóõ][c¢©]+[(k|<{(|x]+(suck|sak|suk)*[k]*(er|ers|a|az|as)*\\b",

  # "cunt"
  "\\b[kc¢©(][u|µüúû]*nt[zs]*\\b",

  # "dick"
  "\\b[d][1!|ïíì][c¢©(][xk|<{(][(head)]*[zs]*\\b",

  # derogatory term for homosexual
  "\\b[f|=ƒ][a@4äáåe]g[g]*[ioa]*[t]*[zs]*\\b",

  # "hoe"
  "\\bh[o0øöóõ][e3€ëéê][zs]*\\b",

  # "hore"
  "\\bh[o0øöóõ]r[e3€ëéê]*[zs]*\\b",

  # "kike"
  "\\b[k|<{(][i1!ïíìy][k|<{(][e3€ëéê][zs]*\\b",

  # racial slur
  "\\bn[i1!ïíì]gg[e3€ëéê|@a4äáå][r]*[zs]*\\b",

  # "knob"
  "\\bknob[(head)]*[zs]*\\b",

  # "lesbo"
  "\\blesbo[sz]*\\b",

  # "minger"
  "\\bming[(a|er)]+(s|z)*\\b",

  # "moron"
  "\\bm[o|u]ron(ic|s|z)*\\b",

  # "muff"
  "\\bmuff\\b",

  # "nonce"
  "\\bnonce\\b",

  # "nympho"
  "\\bnympho\\w*\\b",

  # "pecker"
  "\\bp[e3€ëéê]ck[ae]?[rs]*\\b",

  # "pedo"
  "\\bp[e3€ëéê]do[philf]*[e]*[zs]*\\b",

  # "pikey
  "\\bpik(i|is|ey|ies|eys|eyz|iez|iz)+\\b",

  # "pimp"
  "\\bpimp(s|ing|in|z|ed)*\\b",

  # "piss"
  "\\bp[i1!|ïíì][s5$§z][s5$§]+(in|ing|er|a|ers|erz)*\\b",

  # "poofter"
  "\\bpooft(er|ers|as|az)+\\b",

  # "prick"
  "\\bprick[zs]*\\b",

  # "puke"
  "\\bpuk[e]*(s|z|ing|ed)*\\b",

  # "pussy"
  "\\bp[u|µüúû][s5$§z][s5$§z][@a4äáå]*[y¥][zs]*\\b",

  # "queef"
  "\\bqu[e]+[a]*f(s|z|ing|ed)*\\b",

  # "shag"
  "\\bshag(ging|gin|ged)*\\b",

  # "skank"
  "\\bskank[yzs]*\\b",

  # "slag"
  "\\bslag[zs]*\\b",

  # "slut"
  "\\b[s5$§z]l[uµüúû][t7+†](i|y)*[zs]*\\b",

  # "sod"
  "\\bsod[d]*[sz]*(ing)*\\b",

  # "spastic"
  "\\bspast(ic|ics|icz)*\\b",

  # "retard"
  "\\bretard[zs]*\\b",

  # "tits"
  "\\btit[t]*(i|ies|ay|ays|ayz)*\\b",

  # "tosser"
  "\\btosser[sz]*\\b",

  # "tranny"
  "\\btr[a@4äáå]nn(y|ies|iez)+\\b",

  # "turd"
  "\\bturd[sz]*\\b",

  # "twat"
  "\\b[t7+†]w[a@4äáå][t7+†][zs]*\\b",

  # "wank"
  "\\bw[a@4äáå]n[k|<{(](z|er|ers|ing|az|a|ed)*\\b",

  # "whore"
  "\\b(cam|man|m)*wh[o0øöóõ]?r[e3€ëéê]*(d|s|z|ing)*\\b"

)
```


# KWIC

```{r}
# Australia
t0 <- Sys.time()
df <- audf

kwic_results <- quanteda::kwic(quanteda::tokens(stringi::stri_split_fixed(df$ltext, " ")), pattern = patterns, valuetype="regex") %>%
  as.data.frame() %>%
  dplyr::select(-from, -to) %>%
  dplyr::mutate(code = "au")

# save
base::saveRDS(kwic_results, file = here::here("tables", "kwic_audf_raw.rda"))
t1 <- Sys.time()
t1-t0

# inspect
head(kwic_results, 20); names(table(kwic_results$keyword)); nrow(kwic_results)
```

```{r}
# United Kingdom
t0 <- Sys.time()
df <- gbdf

kwic_results <- quanteda::kwic(quanteda::tokens(stringi::stri_split_fixed(df$ltext, " ")), pattern = patterns, valuetype="regex") %>%
  as.data.frame() %>%
  dplyr::select(-from, -to) %>%
  dplyr::mutate(code = "gb")

# save
base::saveRDS(kwic_results, file = here::here("tables", "kwic_gbdf_raw.rda"))
t1 <- Sys.time()
t1-t0

# inspect
head(kwic_results, 20); names(table(kwic_results$keyword)); nrow(kwic_results)
```


```{r}
# United States
t0 <- Sys.time()
df <- usdf

kwic_results <- quanteda::kwic(quanteda::tokens(stringi::stri_split_fixed(df$ltext, " ")), pattern = patterns, valuetype="regex") %>%
  as.data.frame() %>%
  dplyr::select(-from, -to) %>%
  dplyr::mutate(code = "us")

# save
base::saveRDS(kwic_results, file = here::here("tables", "kwic_usdf_raw.rda"))
t1 <- Sys.time()
t1-t0

# inspect
head(kwic_results, 20); names(table(kwic_results$keyword)); nrow(kwic_results)
```


# Load and kwics

```{r}
aukwic  <- base::readRDS(file = here::here("tables", "kwic_audf_raw.rda"))
gbkwic  <- base::readRDS(file = here::here("tables", "kwic_gbdf_raw.rda"))
uskwic  <- base::readRDS(file = here::here("tables", "kwic_usdf_raw.rda"))
kwic_results <- rbind(aukwic, gbkwic, uskwic)
# inspect
str(kwic_results)
```



# Clean kiwc

```{r}
kwicdf_annotated <- kwic_results %>%
#  dplyr::filter() %>% 
  dplyr::mutate(lemma = dplyr::case_when(pattern == "\\b(dumb|stupid|lazy|worthless|useless|brain|dead|jack)*[a@4äáå]r[s5$§z][e3€ëéê][h]?[o0øöóõ]*[l1£][e3€ëéê]*[s5$§z]*\\b" ~ "arsehole/s",
pattern == "\\b(dumb|stupid|lazy|worthless|useless|brain|dead|jack)*[a@4äáå][s5$§z]{2,}[h]?[o0øöóõ]*[l1|£][e3€ëéê]*[s5$§z]*\\b" ~ "ass/asshole/s",
pattern == "\\b[b8ß|3][i1!|ïíì]+[a@4äáå]*[t7+†][c¢©(][h](es|ez|ing|ed)*\\b" ~ "bitch",
pattern == "\\b[b8ß|3][a@4äáå][s5$§z][t7+†][a@4äáå]r[d][o]*(s|z)*\\b" ~ "bastard",
pattern == "\\b[b8ß|3][e3€ëéê][a@4äáå]n[e3€ëéê]r(s|z)*\\b" ~ "beaner",
pattern == "\\b[b8ß|3][e3€ëéê]ll[e3€ëéê]nd(s|z)*\\b" ~ "bellend",
pattern == "\\b[b8ß|3][1!|ïíì]mb[o0øöóõ](s|z)*\\b" ~ "bimbo",
pattern == "\\bbl[o0øöóõ]{2,}d[iy¥](ed)*\\b" ~ "bloody",
pattern == "\\b[8ß|3][o0øöóõ]ll[o0øöóõiïíì][xc¢©(k|<{(]+[s5$§z]?\\b" ~ "bollocks",
pattern == "\\bboner[s]*\\b" ~ "boner",
pattern == "\\b[8ß|3][o0øöóõ]n[k|<{(](in|ing)*\\b" ~ "bonk",
pattern == "\\b[8ß|3][o0øöóõ]{2,}[b8ß|3][ie]*[s5$§z]?\\b" ~ "boobs",
pattern == "\\b[8ß|3][u|µüúû]gg[e3€ëéê]r(ing|s|z)*\\b" ~ "bugger",
pattern == "\\b[b8ß|3][u|µüúû]ll[s5$§z]h[1!|ïíì]+[t7+†]*\\b" ~ "bullshit",
pattern == "\\b[b8ß3][uµüúû][t7+†][t7+†][sz]*(face|head|wit|whipe|hole|h)*[hl]*[sz]*\\b" ~ "butt",
pattern == "\\b(god)*damn\\b" ~ "damn",
pattern == "\\bdarki(es)*\\b" ~ "darkie",
pattern == "\\b(bull)*d[iy]*ke(s|z)*\\b" ~ "dike",
pattern == "\\bdildo(s|z)*\\b" ~ "dildo",
pattern == "\\bdork(s|z)*\\b" ~ "dork",
pattern == "\\beff(ing|in|ed|d)*\\b" ~ "eff",
pattern == "\\bfann(y|ies)+\\b" ~ "fanny",
pattern == "\\bfart(s|z|ing|in|ed)*\\b" ~ "fart",
pattern == "\\bfrig(g|gin|ging|ged|gs)*\\b" ~ "frig",
pattern == "\\b(cluster|head|mother|motha|mutha|mada|cock|mom|mum|daddy|father|sister|brother)*[f=ƒ][uµüúû|@a4äáå|e3€ëéê|o0øöóõ|*]*[c¢©(]*[k|<{(][e3€ëéê]*[r]*(head|face|wit|ing|er|a|ed|ers|az)*\\b" ~ "fuck",
pattern == "\\b[f=ƒ][c¢©(*k<{(uµüúû*]+(ing|er|a|ed|ers|az)*\\b" ~ "fuck",
pattern == "\\bf\\b" ~ "fuck",
pattern == "\\bgash\\b" ~ "gash",
pattern == "\\bg[o]*ok(s|z)*\\b" ~ "gook",
pattern == "\\bidiot(s|z)*\\b" ~ "idiot",
pattern == "\\bjacka[s5$§z][s5$§z]\\b" ~ "jackass",
pattern == "\\bjap[zs]*\\b" ~ "jap",
pattern == "\\bjerk(s|z|in|ing|ed)*\\b" ~ "jerk",
pattern == "\\bji[s5$§z][s5$§z]+\\b" ~ "jiss",
pattern == "\\bjug[g]*[s5$§z]*\\b" ~ "jug",
pattern == "\\b[(dip)]*[s5$§z]h[1!|ïíì]+[t7+†]*(ing|e|in|er|a|ed|ers|az|s|z)*\\b" ~ "shit",
pattern == "\\bktfo\\b" ~ "online",
pattern == "\\bstfu\\b" ~ "online",
pattern == "\\bgtfo\\b" ~ "online",
pattern == "\\bngaf\\b" ~ "online",
pattern == "\\bdgaf\\b" ~ "online",
pattern == "\\bffs\\b" ~ "online",
pattern == "\\bfml\\b" ~ "online",
pattern == "\\bomfg\\b" ~ "online",
pattern == "\\baf\\b" ~ "online",
pattern == "\\btf\\b" ~ "online",
pattern == "\\bwtf\\b" ~ "online",
pattern == "\\blmao\\b" ~ "online",
pattern == "\\blmfao\\b" ~ "online",
pattern == "\\brofl\\b" ~ "online",
pattern == "\\bch[i]*nk[zs]*\\b" ~ "chink",
pattern == "\\bcoon[zs]*\\b" ~ "coon",
pattern == "\\b[bull]*crap(ping|ped|s|z|pin)*\\b" ~ "crap",
pattern == "\\bcum(ming)*\\b" ~ "cum",
pattern == "\\bc[o0øöóõ][c¢©]+[(k|<{(|x]+(suck|sak|suk)*[k]*(er|ers|a|az|as)*\\b" ~ "cock",
pattern == "\\b[kc¢©(][u|µüúû]*nt[zs]*\\b" ~ "cunt",
pattern == "\\b[d][1!|ïíì][c¢©(][xk|<{(][(head)]*[zs]*\\b" ~ "dick",
pattern == "\\b[f|=ƒ][a@4äáåe]g[g]*[ioa]*[t]*[zs]*\\b" ~ "fag",
pattern == "\\bh[o0øöóõ][e3€ëéê][zs]*\\b" ~ "hoe",
pattern == "\\bh[o0øöóõ]r[e3€ëéê]*[zs]*\\b" ~ "whore",
pattern == "\\b[k|<{(][i1!ïíìy][k|<{(][e3€ëéê][zs]*\\b" ~ "kike",
pattern == "\\bn[i1!ïíì]gg[e3€ëéê|@a4äáå][r]*[zs]*\\b" ~ "nigger",
pattern == "\\bknob[(head)]*[zs]*\\b" ~ "knob",
pattern == "\\blesbo[sz]*\\b" ~ "lesbo",
pattern == "\\bming[(a|er)]+(s|z)*\\b" ~ "minger",
pattern == "\\bm[o|u]ron(ic|s|z)*\\b" ~ "moron",
pattern == "\\bmuff\\b" ~ "muff",
pattern == "\\bnonce\\b" ~ "nonce",
pattern == "\\bnympho\\w*\\b" ~ "nympho",
pattern == "\\bp[e3€ëéê]ck[ae]?[rs]*\\b" ~ "pecker",
pattern == "\\bp[e3€ëéê]do[philf]*[e]*[zs]*\\b" ~ "pedo",
pattern == "\\bpik(i|is|ey|ies|eys|eyz|iez|iz)+\\b" ~ "pikey",
pattern == "\\bpimp(s|ing|in|z|ed)*\\b" ~ "pimp",
pattern == "\\bp[i1!|ïíì][s5$§z][s5$§]+(in|ing|er|a|ers|erz)*\\b" ~ "piss",
pattern == "\\bpooft(er|ers|as|az)+\\b" ~ "poofter",
pattern == "\\bprick[zs]*\\b" ~ "prick",
pattern == "\\bpuk[e]*(s|z|ing|ed)*\\b" ~ "puke",
pattern == "\\bp[u|µüúû][s5$§z][s5$§z][@a4äáå]*[y¥][zs]*\\b" ~ "pussy",
pattern == "\\bqu[e]+[a]*f(s|z|ing|ed)*\\b" ~ "queef",
pattern == "\\bshag(ging|gin|ged)*\\b" ~ "shag",
pattern == "\\bskank[yzs]*\\b" ~ "skank",
pattern == "\\bslag[zs]*\\b" ~ "slag",
pattern == "\\b[s5$§z]l[uµüúû][t7+†](i|y)*[zs]*\\b" ~ "slut",
pattern == "\\bsod[d]*[sz]*(ing)*\\b" ~ "sod",
pattern == "\\bspast(ic|ics|icz)*\\b" ~ "spastic",
pattern == "\\bretard[zs]*\\b" ~ "retard",
pattern == "\\btit[t]*(i|ies|ay|ays|ayz)*\\b" ~ "tits",
pattern == "\\btosser[sz]*\\b" ~ "tosser",
pattern == "\\btr[a@4äáå]nn(y|ies|iez)+\\b" ~ "tranny",
pattern == "\\bturd[sz]*\\b" ~ "turd",
pattern == "\\b[t7+†]w[a@4äáå][t7+†][zs]*\\b" ~ "twat",
pattern == "\\bw[a@4äáå]n[k|<{(](z|er|ers|ing|az|a|ed)*\\b" ~ "wank",
pattern == "\\b(cam|man|m)*wh[o0øöóõ]?r[e3€ëéê]*(d|s|z|ing)*\\b" ~ "whore",
T ~ pattern))
# inspect
names(table(kwicdf_annotated$lemma))
```

check size

```{r}
nrow(kwicdf_annotated)
```


clean keywords

```{r}
kwicdf_annotated <- kwicdf_annotated %>%
  mutate(
    # save original keyword
    keyword_original = keyword,
    
    # clean keyword
    keyword = keyword %>%
      str_remove("^\\W*") %>%          # remove leading non-word chars
      str_remove("(?<!f)\\W*$")        # remove trailing non-word chars unless after "f"
  ) %>%
  filter(
    # remove unwanted patterns
    !str_detect(keyword, "fake"),
    !str_detect(keyword, "°f|˚f|\\*f"),
    !str_detect(keyword, "-\\w{4}-\\w{4}-\\w{4}"),    # passwords
    !str_detect(keyword, "\\bf-\\d{1,3}’?\\w?\\b"),   # f-15, f-22, etc.
    !str_detect(keyword, "\\bm.{1,2}f\\b"),           #m/f
    !str_detect(keyword, "\\bf/\\d")
  )
# inspect
names(table(kwicdf_annotated$keyword))
```


check keywords

```{r}
names(table(kwicdf_annotated$keyword))

keyword_test <- as.data.frame(names(table(kwicdf_annotated$keyword))) %>%
  dplyr::rename(keyword = 1)

#write_xlsx(keyword_test, here::here("tables", "keyword_test.xlsx"))
```


clean keywords

```{r}
kwicdf_clean <- kwicdf_annotated %>%
  # Retain rows where 'lemma' is 'hoe' and 'pre' ends with specified phrases
  filter(!(lemma == "hoe" & !str_detect(pre, "(such a( \\w+)?|other|is a|that( \\w+)?)\\b$")))

bad_keywords <- c(
  "1.fc", "10:30pm(f.t", "15.8003", "19/f", "3008", "4-tit", "70'f", "8008.6",
  "a-b-c-d-e-f", "b..e..a..u..t..i.f..u..l", "b.f.b.t.g", "b/f", "c.m.f.", 
  "cadar/f.", "f(ruitjuice", "f(x", "f)", "f)inance", "j.f.k", "key={gg", 
  "kung-fu", "kung-fu/martial", "l-i-f-e", "l.i.f.e", "m-f,", "m-f.", "m-f/", 
  "m/f", "m/f.", "m+f", "mettraux/f.", "n-f-t", "r.e.f.", "shí", "shí'kis", 
  "shì-sheanamhair", "u-f-ooooo", "u.f.o's", "u=u", "v.i.f", "v.i.f!", 
  "w.e.f.", "w.e.f.?🣯‍♂️", "wold]f", "x100-f", "y.f.n.r.n", "ym=f", "λf=c", 
  "️‍🔯f", "少しビックリしてます。f(", 
  "手数料がすごいのに皆さんちょっとおかしい行動とってますよね。f"
)

kwicdf_clean <- kwicdf_clean %>%
  # filter out unwanted keywords
  filter(!keyword %in% bad_keywords) %>%
  # Remove rows where 'keyword' contains specific unwanted patterns
  filter(!str_detect(keyword, "fak(r|er|ing|ers|ed|e)+")) %>%
  filter(!str_detect(keyword, "fk(r|er|ing|ers|ed|e)+")) %>%
  filter(!str_detect(keyword, "\\w\\+f$")) %>%
  filter(!str_detect(keyword, "n\\|f")) %>%
  filter(!str_detect(keyword, "^\\+f$")) %>%
  filter(!str_detect(keyword, "=(x|a|r|v|c|k|f)")) %>%
  filter(!str_detect(keyword, "(x|a|r|v|c|k|f)=")) %>%
  filter(!str_detect(keyword, "feg(i|o)")) %>%
  filter(!str_detect(keyword, "^feek.*")) %>%
  filter(!str_detect(keyword, "(x|a|r|v|c|k|f)\\+")) %>%
  filter(!str_detect(keyword, "\\+(x|a|r|v|c|k|f)"))  %>%
  dplyr::filter(!str_detect(keyword, "^\\$")) %>%
  dplyr::filter(!str_detect(keyword, "\\d{3}")) %>%
  dplyr::filter(!str_detect(keyword, "\\d{2}=")) %>%
  dplyr::filter(!str_detect(keyword, "fag(a|o)+")) %>%
  dplyr::filter(!str_detect(keyword, "fauk\\w*")) %>%
  dplyr::filter(!str_detect(keyword, "hoess")) %>%
  dplyr::filter(!str_detect(keyword, "z=u")) %>%
  dplyr::filter(!str_detect(keyword, "\\+jug")) %>%
  dplyr::filter(!str_detect(keyword, "2=u")) %>%
  dplyr::filter(!str_detect(keyword, "b=ok")) %>%
  dplyr::filter(!str_detect(keyword, "st=ok")) %>%
  dplyr::filter(!str_detect(keyword, "stat=u")) %>%
  dplyr::filter(!str_detect(keyword, "t=0k")) %>%
  dplyr::filter(!str_detect(keyword, "^feak\\*")) %>%
  dplyr::filter(!str_detect(keyword, "^fc+$")) %>%
  dplyr::filter(!str_detect(keyword, "^f[c]+a.*$")) %>%
  dplyr::filter(!str_detect(keyword, "^fauc.*$")) %>%
  dplyr::filter(!str_detect(keyword, "^f\\$\\d+$")) %>%
  dplyr::filter(!str_detect(keyword, "°f"))

kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'lemma' is 'jerk' and 'pre' ends with 'knee' or 'chest'
  filter(!(lemma == "jerk" & str_detect(pre, "(knee|chest)$"))) 


kwicdf_clean <- kwicdf_clean %>%
  # Retain rows where 'lemma' is 'eff' and 'post' starts with 'you', 'it', 'off', or 'up'
  filter(!(lemma == "eff" & !str_detect(post, "^(you|it|off|up)"))) 

kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'lemma' is 'f' unless 'post' starts with specified pronouns or similar words or pre ends with flying
  filter(!(keyword == "f" & !str_detect(post, "^(king|me|you|it|this|that|these|those|him|her|us|them)\\b")| str_detect(pre, "(flying)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'lemma' is 'crap' and 'pre' ends with specified phrases
  filter(!(lemma == "crap" & str_detect(pre, "(metal|poker|roulette)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'lemma' is 'dyke' and 'pre' does not end with specified phrases
  filter(!(lemma == "dyke" & !str_detect(pre, "\\b(a|like|butch|bull|all|fags|as|fucking|club)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'lemma' is 'faggot' and 'pre' ends with specified phrases
  filter(!(keyword == "faggot" & str_detect(post, "(bearer)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'keyword' is 'fag' and 'pre'  ends with specified phrases
  filter(!(keyword == "fags" & str_detect(pre, "\\b(of|and|buy|the|few|candy)\\b$") | str_detect(post, "^(to)\\b")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'fk' and 'pre' ends with specified phrases
  filter(!(keyword == "fk" & str_detect(pre, "(bryne)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'jiss' and 'pre' ends with specified phrases
  filter(!(keyword == "jizz" & str_detect(pre, "\\b(dns)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'fu' and 'pre' ends with specified phrases
  filter(!(keyword == "fu" & str_detect(pre, "(k(ou)ng)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'keyword' is 'knob' and 'post' does not end with specified phrases
  filter(!(lemma == "knob" & !str_detect(post, "^\\b(head[s]?)\\b")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'pecker' and 'pre' ends with specified phrases
  filter(!(keyword == "pecker" & str_detect(pre, "\\b(a|wood|of|so)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Retain rows where 'lemma' is 'sod' and 'pre' ends with a xxx xxx
  filter(!(lemma == "sod" & !str_detect(pre, "\\ba[n]{0,1}( \\w+)?( \\w+)?$"))) 

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'sodd' and 'post' starts with specified phrases
  filter(!(keyword == "sodd" & str_detect(post, "^\\b(s)\\b")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'sodd' and 'pre' ends with specified phrases
  filter(!(keyword == "sods" & str_detect(pre, "\\band\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'keyword' is 'tf' and 'pre' does not end with specified phrases
  filter(!(lemma == "tf" & !str_detect(pre, "\\b(how)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Retain rows where 'keyword' is 'wanka' and 'pre' ends with specified phrases
  filter(!(keyword == "wanka" & !str_detect(pre, "(such a( \\w+)?|other|is a|that( \\w+)?)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'whor' and 'pre' ends with specified phrases
  filter(!(keyword == "whor" & str_detect(pre, "\\b(casteism)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Retain rows where 'lemma' is 'jitt' and 'post' starts with music
  filter(!(lemma == "jizz" & !str_detect(post, "^music"))) 


kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is f-14 etc
  filter(!(str_detect(keyword, "f-\\d")))

kwicdf_clean <- kwicdf_clean %>%
  # remove \" from 'keyword'
  mutate(keyword = gsub("(?<!f)[^A-Za-z0-9_]", "", keyword, perl = TRUE)) %>%
  # remove  from 'keyword'
  mutate(keyword = str_remove_all(keyword, "\\d.f")) %>%
  # remove * from 'keyword'
  mutate(keyword = str_remove_all(keyword, "\\b\\d\\W{0,1}\\b"))


# inspect
#kwicdf_clean[which(kwicdf_clean$keyword == "whrs"),]
names(table(kwicdf_clean$keyword))
```

# Remove duplicate rows using dplyr

```{r}
nrow(kwicdf_clean)
kwicdf_clean <- kwicdf_clean %>% dplyr::select(-pattern)
kwicdf_clean <- kwicdf_clean %>% dplyr::distinct()
nrow(kwicdf_clean)
```


check kwics

```{r}
kwicdf_clean[which(kwicdf_clean$keyword == "jizz"),] 
```


# Save KWIC
°f

```{r}
base::saveRDS(kwicdf_clean, file = here::here("tables", "kwicdf_clean.rda"))
```




# Outro

```{r}
sessionInfo()
```


