---
title: "F%$# Twitter. A corpus-based analysis of vulgar language on Twitter - Part 3: Analysis"
author: "Martin Schweinberger"
date: "`r Sys.Date()`"
output: html_document
---


# Introduction

This document shows the analysis of swear words in the Australian, UK, and US Twitterspheres

# Preparation

Install packages

```{r inst, eval = F}
# install packages from CRAN
install.packages(c("dplyr", "here", "stringr", "quanteda", "tidytext", "sentimentr", "writexl", "ggplot2", "Hmisc", "countrycode", "ggimage", "cfa", "forcats", "tm", "slam", "report", "seededlda", "Boruta", "reshape2", "rms", "lme4", "sjPlot", "car"))

install.packages("topicmodels", type = "source")

# install ggflags package from GitHub
install.packages("devtools")
devtools::install_github('rensa/ggflags')

```

Activate packages

```{r}
library(dplyr)
library(here)
library(stringr)
library(tidytext)
library(quanteda)
library(sentimentr)
library(writexl)
library(ggplot2)
library(Hmisc)
library(cfa)
library(topicmodels)
library(countrycode)
library(seededlda)
library(reshape2)
library(ggflags)
library(report)
library(Boruta)
library(rms)
library(lme4)
library(sjPlot)
library(car)
library(forcats)  # For reordering
```

# Processing

Load data

```{r load}
twdat  <- base::readRDS(file = here::here("data", "twdat.rda"))
kwicdf <- base::readRDS(file = here::here("tables", "kwicdf_clean.rda"))
# inspect
str(twdat); str(kwicdf)
```


# Inferential statistics

```{r}
kwicdat <- kwicdf %>%
  dplyr::group_by(code, docname) %>%
  dplyr::summarise(vulgar = n())
# inspect
head(kwicdat)
```



```{r}
dat <- dplyr::left_join(twdat, kwicdat, by = c("docname", "code"))
# inspect
head(dat); table(dat$code)
```

# Table1

```{r}
Table1 <- dat %>%
  tidyr::replace_na(list(vulgar = 0)) %>%
  dplyr::group_by(code) %>%
  dplyr::summarise(Tokens = sum(words),
                   Tweets = n(),
                   Users = length(names(table(user_id))),
                   VulgarTokens = sum(vulgar),
                   VulgarTweets = sum(ifelse(vulgar > 0, 1, 0)),
                   MeanLengthTweet = round(Tokens/Tweets, 1),
                   PercentVulgarTweets = round(VulgarTweets/Tweets * 100, 2),
                   PercetVulgarTokens = round(VulgarTokens/Tokens*100, 2))
# inspect
Table1
```

```{r}
sum(Table1[,2])
sum(Table1[,3])
sum(Table1[,4])
sum(Table1[,2])/sum(Table1[,3])
```



```{r}
# tweets
(3581+19005+97748)/(99404+538661+2090972)*100
# tokens
(3906+20655+108175)/(1449292+7883971+27398975)*100
```


```{r}
# vulgar tweets au
3581/99404*100
# vulgar tweets uk
19005/538661*100
# vulgar tweets us
97748/2090972*100
```


```{r}
# vulgar tokens au
3906/1449292*100
# vulgar tokens uk
20655/7883971*100
# vulgar tokens us
108175/27398975*100
```



```{r}
Table1b <- dat %>%
  tidyr::replace_na(list(vulgar = 0)) %>%
  dplyr::group_by(code, user_id) %>%
  dplyr::summarise(vulgar = sum(ifelse(vulgar > 0, 1, 0))) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(code) %>%
  dplyr::summarise(users = n(),
                   vulgarusers = sum(vulgar),
                   percent = round(vulgarusers/users*100, 1))
# inspect
Table1b
```


data prep
 
```{r}
sdat <- dat %>%
  dplyr::ungroup() %>%
  dplyr::mutate(wordsonly = tolower(wordsonly)) %>%
  dplyr::select(-tweet_retrieved_at, -conversation_id, -lang, -source, -possibly_sensitive, -reply_settings, -withheld_copyright, -tweet_withheld_country_codes, -tweet_link, -user_retrieved_at, -username, -name, -location, -user_withheld_country_codes, -user_link, -cleantext, -transformed_text, -country, -text, -replied_to_tweet_id, -var) %>%  
  dplyr::mutate(user_created_at = stringr::str_remove_all(user_created_at, "-.*"),
                retweeted_tweet_id = ifelse(is.na(retweeted_tweet_id), "original", "retweet"),
                quoted_tweet_id = ifelse(is.na(quoted_tweet_id), "containsquote", "noquote"),
                id = 1:nrow(.)) %>%  
  tidyr::replace_na(list(vulgar = 0))  %>%
  dplyr::rename(retweet = retweeted_tweet_id,
                quoted = quoted_tweet_id,
                tweets = tweet_count,
                listed = listed_count,
                usersince = user_created_at) %>%
  dplyr::filter(words >= 5)
# inspect
head(sdat);nrow(sdat)
```


# Topic Modelling


```{r eval = F}
sdat$wordsonly %>%
  # tokenise
  quanteda::tokens(remove_punct = T,
                   remove_symbols = T,
                   remove_numbers = T,
                   remove_url = T) %>% 
  # remove stop words
  quanteda::tokens_select(pattern = stopwords("en"), selection = "remove") %>%
  quanteda::tokens_select(pattern = stopwords("es"), selection = "remove") %>%
  quanteda::tokens_select(pattern = "\\b(?!i$|ai$|ml$|vr$|tv$|blm$|cat$|dog$|bus$|car$|sex$|nsfw$|law$|gdp$|dm$)[a-z]{1,3}\\b", 
                          selection = "remove", valuetype = "regex") %>%
  # stemming
  quanteda::tokens_wordstem() %>%
  # convert to document-frequency matrix
  quanteda::dfm(tolower = T) -> ctxts
# add docvars
docvars(ctxts, "id") <- sdat$id
# clean data
ctxts <- dfm_subset(ctxts, ntoken(ctxts) > 0)
# inspect data
ctxts[1:5, 1:5]
```

unsupervised LDA

```{r eval = F}
# generate model: change k to different numbers, e.g. 10 or 20 and look for consistencies in the keywords for the topics below.
topicmodels::LDA(ctxts, k = 15, control = list(seed = 1234)) -> ddlda
base::saveRDS(ddlda, file = here::here("tables", "ddlda.rda"))
```

load results of unsupervised lda

```{r eval = F}
ddlda  <- base::readRDS(file = here::here("tables", "ddlda.rda"))
```


```{r eval = F}
# define number of topics
ntopics <- 15
# define number of terms
nterms <- 10
# generate table
tidytext::tidy(ddlda, matrix = "beta") %>%
  dplyr::group_by(topic) %>%
  dplyr::slice_max(beta, n = nterms) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(topic, -beta) %>%
  dplyr::mutate(
    term = paste(term, " (", round(beta, 3), ")", sep = ""),
    topic = paste("topic", topic),
    topic = factor(topic, levels = c(paste("topic", 1:ntopics))),
    top = rep(paste("top", 1:nterms), nrow(.) / nterms),
    top = factor(top, levels = c(paste("top", 1:nterms)))
  ) %>%
  dplyr::select(-beta) %>%
  tidyr::spread(topic, term) -> ddlda_top_terms
ddlda_top_terms
```

extract topics

```{r eval = F}
# extract topics
ddlda_topics <- tidy(ddlda, matrix = "beta")
# inspect
head(ddlda_topics, 20)
```

inspect topics

```{r eval = F}
ddlda_topics %>%
  select(term) %>%
  unique() %>%
  filter(str_detect(term, "bridg"))
```


seeded topic modelling

```{r eval = F}
# semisupervised LDA
dict <- dictionary(list(
  crime         = c("crime", "murder", "polic", "violenc", "theft", "assault", "shoot", "arrest", "prison", "gun"),
  employment    = c("job", "employ", "work", "hire", "wage", "career", "unemploy", "salari", "intern", "boss"),
  entertainment = c("music", "film", "movi", "show", "celebr", "tv", "netflix", "seri", "concert", "award"),
  finance       = c("money", "bank", "stock", "invest", "crypt", "bitcoin", "market", "fund", "trade", "dollar"),
  economy       = c("econom", "inflation", "recess", "gdp", "tax", "budget", "spend", "debt", "growth", "unemploy"),
  fashion       = c("fashion", "style", "trend", "wear", "design", "outfit", "brand", "cloth", "runway", "makeup"),
  food          = c("food", "eat", "cook", "drink", "restaur", "dinner", "snack", "meal", "beer", "wine"),
  travel        = c("travel", "trip", "vacat", "flight", "hotel", "tourism", "holiday", "tour", "airport", "journey"),
  gaming        = c("game", "gamer", "play", "console", "esport", "xbox", "playstat", "nintendo", "stream", "twitch"),
  science       = c("scienc", "research", "experi", "lab", "discoveri", "theori", "univers", "evidenc", "space", "astronom"),
  relationships = c("love", "relationship", "date", "friend", "partner", "romanc", "crush", "marriag", "coupl", "divorc"),
  memes         = c("meme", "funni", "joke", "gif", "trend", "lol", "haha", "humor", "parodi", "troll"),
  business      = c("busi", "market", "brand", "entrepreneur", "startup", "compani", "corpor", "manag", "profit", "industr"),
  mental_health = c("stress", "anxieti", "depress", "mind", "therapi", "mental", "psycho", "wellb", "selfcar", "suicid"),
  transport     = c("car", "traffic", "train", "bus", "bike", "road", "highway", "metro", "subway", "uber"),
  shopping      = c("shop", "buy", "store", "sale", "discount", "amazon", "cart", "retail", "coupon", "order"),
  activism      = c("right", "protest", "justic", "equal", "chang", "blm", "climat", "march", "activist", "campaign"),
  pets          = c("pet", "dog", "cat", "anim", "vet", "puppi", "kitten", "hamster", "parrot", "adopt"),
  tech          = c("tech", "comput", "ai", "internet", "digit", "data", "app", "cyber", "cloud", "softwar"),
  ai_innovation = c("ai", "ml", "deeplearn", "chatgpt", "neural", "robot", "quantum", "blockchain", "crypto", "vr"),
  medical       = c("medic", "health", "doctor", "hospit", "nurs", "sick", "diseas", "surgeri", "clinic", "treatment"),
  immigration   = c("immigr", "migrat", "border", "visa", "asylum", "refuge", "citizenship", "deport", "migrant", "greencard"),
  foreign       = c("foreign", "diplomat", "global", "intern", "trade", "allianc", "embassi", "sanction", "treati", "war"),
  media         = c("media", "news", "journal", "press", "report", "articl", "editor", "headlin", "outlet", "tv"),
  adult_content = c("porn", "sex", "nsfw", "xxx", "adult", "fetish", "nude", "erot", "onlyfan", "strip"),
  politics      = c("politic", "elect", "vote", "democr", "republic", "senat", "congress", "parliament", "law", "polici"),
  climate       = c("climat", "globalwarm", "sustain", "renew", "green", "pollut", "emiss", "ecolog", "solar", "carbon"),
  sports        = c("sport", "team", "match", "game", "champion", "leagu", "soccer", "footbal", "basketbal", "tenni"),
  education     = c("school", "univers", "student", "teacher", "class", "learn", "curriculum", "exam", "degree", "scholarship"),
  social_media  = c("twitter", "tweet", "facebook", "insta", "tiktok", "hashtag", "post", "dm", "follow", "like"),
  military      = c("militari", "war", "armi", "navy", "soldier", "defens", "weapon", "nuclear", "drone", "conflict"),
  identity      = c("gender", "race", "lgbt", "queer", "trans", "ethnic", "inclus", "divers", "equal", "ident")
))
tmod_slda <- seededlda::textmodel_seededlda(ctxts,
  dict,
  residual = TRUE,
  min_termfreq = 2
)
# inspect
seededlda::terms(tmod_slda)

# save
base::saveRDS(tmod_slda, file = here::here("tables", "tmod_slda.rda"))

# generate data frame
data.frame(tmod_slda$data@docvars$id, seededlda::topics(tmod_slda)) %>%
  dplyr::rename(id = 1,
                Topic = 2) -> topic_df
# save
base::saveRDS(topic_df, file = here::here("tables", "topic_df.rda"))
# inspect
head(topic_df)
```

load seeded lda results

```{r}
topic_df  <- base::readRDS(file = here::here("tables", "topic_df.rda"))
```

combine topics and data

```{r}
rdat <- dplyr::left_join(sdat, topic_df, by = "id") %>%
  dplyr::mutate(
    Topic = as.character(Topic),   # convert factor to character
    Topic = ifelse(is.na(Topic), "no topic", Topic)
  )
  #dplyr::filter(!is.na(Topic))
# inspect
head(rdat);nrow(sdat);nrow(rdat)

```

Topic overview table

```{r}
# Overview table with counts and percentages
topic_overview <- rdat %>%
  group_by(Topic) %>%                       # group by Topic
  summarise(Frequency = n(), .groups = "drop") %>%  # count occurrences
  mutate(Percentage = round((Frequency / sum(Frequency)) * 100, 1)) %>%  # calculate percentage
  arrange(desc(Frequency))                   # optional: sort by frequency

# View the table
topic_overview
```




# Time

```{r}
# define timezone offsets relative to UTC
# adjust if you want to account for daylight saving
offsets <- c(
  us = -5,   # Eastern Standard Time (UTC-5)
  gb = +1,   # British Summer Time (UTC+1)
  au = +10   # Australian Eastern Standard Time (UTC+10)
)

rdat <- rdat %>%
  mutate(
    code = tolower(trimws(code)),  # make sure codes match offsets names
    hour_utc = as.numeric(str_extract(tweet_created_at, "(?<=T)\\d{2}")),
    time = (hour_utc + offsets[code]) %% 24
  ) %>%
  select(-hour_utc)

table(rdat$code, rdat$time)
```



```{r}
bdat <- rdat %>%
  # normal
  dplyr::select(-ltext)  %>%
  dplyr::mutate(vulgar = ifelse(vulgar > 0 , 1, 0)) %>%
  dplyr::mutate(logtweets = log(tweets),
                logfollowers = log(followers_count+0.01),
                logfollowing = log(following_count+0.01),
                loglisted = log(listed+0.01),
                logretweets = log(retweet_count+0.01),
                logreplies = log(reply_count+0.01),
                loglikes = log(like_count+0.01),
                logquotes = log(quote_count+0.01),
                topic = factor(Topic),
                vulgar = factor(vulgar),
                user = factor(user_id),
                time = factor(time)) %>%
  dplyr::select(-tweets, -followers_count, -following_count, -listed, -retweet_count, -reply_count, -like_count, -user_id, -quote_count, -tweet_id, -Topic, -tweet_created_at) %>%
  dplyr::ungroup()
# inspect
head(bdat)
```


reformat time

```{r}
bdat %>% 
  dplyr::ungroup() %>%
  dplyr::filter(code == "au")  %>% 
  dplyr::group_by(time) %>% 
  dplyr::summarise(freq = n()) %>% 
  ggplot(aes(x = time, y = freq)) +
  geom_bar(stat = "identity")
```

```{r}
bdat %>% 
  dplyr::ungroup() %>%
  dplyr::filter(code == "gb")  %>% 
  dplyr::group_by(time) %>% 
  dplyr::summarise(freq = n()) %>% 
  ggplot(aes(x = time, y = freq)) +
  geom_bar(stat = "identity")
```

```{r}
bdat %>% 
  dplyr::ungroup() %>%
  dplyr::filter(code == "us")  %>% 
  dplyr::group_by(time) %>% 
  dplyr::summarise(freq = n()) %>% 
  ggplot(aes(x = time, y = freq)) +
  geom_bar(stat = "identity")
```






```{r}
Fig3dat <- bdat %>%
  dplyr::group_by(code, time) %>%
  dplyr::summarise(tweets = n(),
                   vulgar = sum(ifelse(vulgar == "1", 1, 0))) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(code) %>%
  dplyr::mutate(totaltweets = sum(tweets),
                totalvulgar = sum(vulgar)) %>%
  dplyr::ungroup()  %>%
  dplyr::mutate(O11 = vulgar,
                O12 = totalvulgar- O11,
                O21 = tweets-O11,
                O22 = totaltweets-O11-O12-O21,
                R1 = totalvulgar,
                R2 = totaltweets - totalvulgar,
                C1 = tweets,
                C2 = totaltweets - C1)  %>%
  dplyr::mutate(O11exp = C1*R1/totaltweets,
                O11x2 = (O11-O11exp)^2/O11exp,
                phi = sqrt(O11x2/totaltweets)) %>%
  dplyr::mutate(phi = ifelse(O11 > O11exp, phi, -phi))
# inspect
head(Fig3dat)
  
```

Fig3

```{r}
Fig3dat %>%
  dplyr::mutate(code = dplyr::case_when(code == "us" ~ "United States",
                                        code == "au" ~ "Australia",
                                        code == "gb" ~ "United Kingdom",
                                        T ~ code)) %>%
  ggplot(aes(x = time, y = phi, fill = phi)) +
  geom_bar(stat = "identity", color = "gray10") +
  facet_wrap(~code, nrow = 3) +
    theme_bw() +
  scale_fill_gradient2(low = 'blue', mid = 'white', high = 'red', midpoint = 0) +
  scale_x_discrete(breaks = levels(Fig3dat$time), labels = paste0(levels(Fig3dat$time), ":00", sep = "")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 90),
        legend.position = "none") +
  labs(x = "Time of day (local time)", y = "Phi-coefficient")
# save
ggsave(here::here("images", "Fig3_time.png"), width = 15, height = 12, units = "cm", dpi = 600)
```

check what happens in Australia at 6 and 7pm.

```{r}
bdat %>%
  dplyr::filter(code == "au",
                vulgar != 0,
                time == 18|19) %>%
  dplyr::select(wordsonly)
```

```{r}
bdat %>%
  dplyr::filter(code == "au",
                vulgar != 0,
                time == 18|19) %>%
  dplyr::group_by(topic) %>%
  dplyr::summarise(freq = n())
```

# Topics

```{r}
Fig4dat <- bdat %>%
  dplyr::group_by(code, topic) %>%
  dplyr::summarise(tweets = n(),
                   vulgar = sum(ifelse(vulgar == "1", 1, 0))) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(topic) %>%
  dplyr::mutate(totaltweets = sum(tweets),
                totalvulgar = sum(vulgar)) %>%
  dplyr::ungroup()  %>%
  dplyr::mutate(O11 = vulgar,
                O12 = totalvulgar- O11,
                O21 = tweets-O11,
                O22 = totaltweets-O11-O12-O21,
                R1 = totalvulgar,
                R2 = totaltweets - totalvulgar,
                C1 = tweets,
                C2 = totaltweets - C1)  %>%
  dplyr::mutate(O11exp = C1*R1/totaltweets,
                O11x2 = (O11-O11exp)^2/O11exp,
                phi = sqrt(O11x2/totaltweets)) %>%
  dplyr::mutate(phi = ifelse(O11 > O11exp, phi, -phi))
# inspect
head(Fig4dat)
  
```

Fig4

```{r}
Fig4dat %>%
  dplyr::mutate(code = dplyr::case_when(code == "us" ~ "United States",
                                        code == "au" ~ "Australia",
                                        code == "gb" ~ "United Kingdom",
                                        T ~ code)) %>%
  ggplot(aes(x = topic, y = phi, fill = phi)) +
  geom_bar(stat = "identity", color = "gray10") +
  facet_wrap(~code, nrow = 3) +
    theme_bw() +
  scale_fill_gradient2(low = 'blue', mid = 'white', high = 'red', midpoint = 0) +
  #scale_x_discrete(breaks = levels(Fig3dat$topic), labels = paste0(levels(Fig3dat$topic), ":00", sep = "")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 90),
        legend.position = "none") +
  labs(x = "Topic", y = "Phi-coefficient")
# save
ggsave(here::here("images", "Fig4_topics.png"), width = 15, height = 12, units = "cm", dpi = 600)
```


# Boruta

extract sample

```{r}
borutadat <- bdat %>%
  # WARNING: for testing
  dplyr::group_by(code) %>%
  dplyr::sample_n(5000) %>%
  dplyr::ungroup()  %>%
dplyr::select(-docname, -wordsonly, -id)
```



```{r eval = F}
library(Boruta)
# set.seed 
set.seed(20221210)
# initial run
boruta1 <- Boruta(vulgar~.,data=borutadat, maxRuns = 50)
print(boruta1)
```


```{r eval = F}
# extract decision
getConfirmedFormula(boruta1)
```

```{r eval = T}
boruta2 <-Boruta(vulgar ~ usersince + words + logtweets + logfollowers + logfollowing + 
    loglisted + logretweets + logreplies + loglikes + logquotes + 
    topic + user, data = borutadat)
print(boruta2)
```


```{r eval = F}
# extract decision
getConfirmedFormula(boruta2)
```

```{r eval = T}
borutadf <- as.data.frame(boruta2$ImpHistory) %>%
  tidyr::gather(Variable, Importance, user:shadowMin) %>%
  dplyr::mutate(Type = ifelse(str_detect(Variable, "shadow"), "Control", "Predictor")) %>%
  dplyr::mutate(Type = factor(Type),
                Variable = factor(Variable))

# inspect
head(borutadf)
```

```{r}
borutadf %>%
  dplyr::group_by(Variable) %>%
  dplyr::summarise(Importance = mean(Importance)) %>%
  dplyr::arrange(-Importance) %>%
  dplyr::pull(Variable)

```



```{r eval = T}
ggplot(borutadf, aes(x = reorder(Variable, Importance, mean), y = Importance, fill = Type)) + 
  geom_boxplot() +
  geom_vline(xintercept=3.5, linetype="dashed", color = "black") +
  scale_fill_manual(values = c("gray80", "gray40")) +
  theme_bw() + 
  theme(legend.position = "top",
        axis.text.x = element_text(angle=90)) +
  labs(x = "Variable")
# save
ggsave(here::here("images", "Fig7.png"))
```


```{r}
base::saveRDS(bdat, file = here::here("data", "bdat.rda"))
```


# Outro

```{r}
sessionInfo()
```

